% =============================================================
%  Complete Academic Peer Review
%  Journal : IEEE Transactions on Circuits and Systems for
%            Video Technology (IEEE TCSVT)
%  Paper   : "CT-to-X-ray Distillation Under Tiny Paired Cohorts:
%             An Evidence-Bounded Reproducible Pilot Study"
%  Date    : 2026-05-02
% =============================================================
\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{mdframed}

% ---------- colour palette ----------
\definecolor{tcsvtblue}{RGB}{0,82,155}
\definecolor{warnorange}{RGB}{200,80,0}
\definecolor{notegreen}{RGB}{0,120,60}
\definecolor{lightgray}{RGB}{240,240,240}

% ---------- section formatting ----------
\titleformat{\section}{\large\bfseries\color{tcsvtblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{tcsvtblue}}{}{0em}{}

% ---------- header / footer ----------
\pagestyle{fancy}
\fancyhf{}
\lhead{\small\textit{IEEE TCSVT — Confidential Peer Review}}
\rhead{\small\textit{Manuscript Review Report}}
\cfoot{\thepage}

% ---------- custom environments ----------
\newmdenv[linecolor=warnorange,backgroundcolor=warnorange!8,
          linewidth=1.5pt,innerleftmargin=8pt,innerrightmargin=8pt,
          innertopmargin=6pt,innerbottommargin=6pt]{majorbox}
\newmdenv[linecolor=notegreen,backgroundcolor=notegreen!6,
          linewidth=1pt,innerleftmargin=8pt,innerrightmargin=8pt,
          innertopmargin=6pt,innerbottommargin=6pt]{minorbox}
\newmdenv[linecolor=tcsvtblue,backgroundcolor=tcsvtblue!5,
          linewidth=1pt,innerleftmargin=8pt,innerrightmargin=8pt,
          innertopmargin=6pt,innerbottommargin=6pt]{infobox}

% ---------- shorthand ----------
\newcommand{\tcsvt}{\textit{IEEE TCSVT}}
\newcommand{\eg}{\textit{e.g.},\ }
\newcommand{\ie}{\textit{i.e.},\ }
\newcommand{\etal}{\textit{et al.}}
\newcommand{\major}[1]{\textbf{\color{warnorange}[Major \##1]}}
\newcommand{\minor}[1]{\textbf{\color{notegreen}[Minor \##1]}}
\newcommand{\typog}[1]{\textbf{\color{gray}[Editorial \##1]}}

% =============================================================
\begin{document}

\begin{titlepage}
  \centering
  \vspace*{2cm}
  {\LARGE\bfseries\color{tcsvtblue}
   IEEE Transactions on Circuits and Systems\\[4pt]
   for Video Technology (IEEE TCSVT)\\[8pt]
   Manuscript Review Report\par}
  \vspace{1.2cm}
  \rule{\linewidth}{1.5pt}\\[0.4cm]
  {\large\bfseries
   ``CT-to-X-ray Distillation Under Tiny Paired Cohorts:\\
   An Evidence-Bounded Reproducible Pilot Study''\par}
  \rule{\linewidth}{0.8pt}\\[0.8cm]
  {\normalsize
  \begin{tabular}{ll}
    \textbf{Review date:}    & 2026-05-02 \\[4pt]
    \textbf{Reviewer:}       & Anonymous (IEEE TCSVT Review Process) \\[4pt]
    \textbf{Recommendation:} & \textbf{\color{warnorange}Major Revision Required} \\[4pt]
    \textbf{Confidence:}     & High \\
  \end{tabular}\par}
  \vspace{1cm}
  \begin{infobox}
  \small\textbf{Scope note.}\ \
  IEEE TCSVT publishes research on circuits, systems, and signal-processing
  algorithms for video-technology applications, including medical video/image
  analysis, deep-learning-based visual recognition, and multi-modal media
  processing. The present manuscript's cross-modality distillation study
  falls within the journal's stated scope, but the severity of the data
  limitations and the absence of positive architectural contributions raise
  fundamental questions about whether the submission meets TCSVT's
  technical-contribution threshold. This report details the conditions
  under which a revised submission could potentially be accepted.
  \end{infobox}
  \vfill
  {\footnotesize\color{gray} This review report is confidential and
  intended solely for the handling editor and the authors.}
\end{titlepage}

% =============================================================
\tableofcontents
\newpage

% =============================================================
\section{Executive Summary and Recommendation}
% =============================================================

\begin{infobox}
\textbf{One-paragraph summary.}\\
The manuscript proposes JDCNet, a teacher–student cross-modality
knowledge-distillation (KD) framework for COVID-19 classification in
which a CT teacher supervises an X-ray student during training while the
deployed model uses X-ray only. The study uses the public
\textit{COVID-19 Image Data Collection} paired subset (26 images, 19
patients, 4-image validation set). The proposed architecture introduces
three optional modules — Dynamic Positional Encoding (DPE), Multi-Head
Relation Aggregation (MHRA), and a Dense Feature Pyramid Network (DFPN)
— on top of a plain logit-KD baseline. The authors honestly acknowledge
that the proposed modules do not improve upon the stripped-down baseline
under any of the reported controls, and they explicitly frame the work as
a ``reproducible pilot protocol'' rather than a validated architecture.
Eight patient-level Monte Carlo resamples provide the primary same-case
evidence; under this protocol, neither cross-modal logit KD nor the
added modules outperform same-modality distillation or student-only
training on balance-sensitive metrics.
\end{infobox}

\vspace{6pt}
\textbf{Recommendation: \color{warnorange}Major Revision Required.}
The manuscript raises a genuine and important research question, maintains
high scientific honesty, and provides a useful reproducibility scaffold.
However, in its current form it cannot be accepted in \tcsvt{} for the
following fundamental reasons, each detailed in Section~\ref{sec:major}:
\begin{enumerate}[leftmargin=2em]
  \item The validation set of \textbf{four images} (three positive,
        one negative) is scientifically insufficient to support any
        comparative ranking, even as a ``feasibility screen''.
  \item The proposed architecture (JDCNet with DPE/MHRA/DFPN)
        \textbf{does not outperform any baseline} on any metric under
        the stronger same-case evaluation.
  \item The paper lacks comparison with any \textbf{state-of-the-art
        cross-modal distillation or multi-modal medical-imaging method}
        from the last three years.
  \item Several \textbf{architectural design choices} are neither
        theoretically motivated nor empirically validated at the required
        depth for a transactions-level paper.
  \item The framing as a ``pilot study'' is appropriate for a workshop
        or short communication, but does not meet the
        \textbf{original-contribution standard} expected by \tcsvt{}.
\end{enumerate}

A revised submission that either (a) substantially enlarges the paired
cohort to provide credible validation support, or (b) reframes the
paper around the reproducible evaluation \emph{protocol} with
demonstrably new methodological or benchmarking contributions, would be
suitable for re-review.

% =============================================================
\section{Detailed Strengths}
% =============================================================

The following strengths are genuine and should be preserved or amplified
in any revision.

\begin{enumerate}[leftmargin=2em]
  \item \textbf{Scientific honesty.}  The paper is unusual in that it
        explicitly reports that its proposed method does not outperform
        simpler controls. This is commendable and rare in deep-learning
        literature.  The evidence hierarchy (fixed-split feasibility
        screen $\to$ repeated same-case resampling as primary evidence)
        is logically sound and clearly communicated.

  \item \textbf{Deployment-realistic problem formulation.}  Framing
        the task as training-only CT supervision with X-ray-only
        deployment is clinically well-motivated and avoids the
        inference-time modality-availability trap that affects most
        multi-modal fusion papers.

  \item \textbf{Patient-level evaluation discipline.}  Splitting at
        the patient level and confirming zero patient overlap across
        folds is methodologically correct and better than many medical
        AI papers that split at the image level.

  \item \textbf{Imbalance-sensitive analysis.}  The paper goes beyond
        accuracy and macro-F1 to report balanced accuracy, MCC, and
        specificity, and correctly explains why PR-AUC is a poor
        primary metric under the existing prevalence regime.

  \item \textbf{Hypothesis-driven experiment structure.}  The five
        explicit hypotheses (H1–H5) and their per-hypothesis
        status table (Table~6) are a model of transparent reporting.
        The tiered experimental design (Tier 1: feasibility, Tier 2:
        mechanism, Tier 3: proposed module) is logically coherent.

  \item \textbf{Reproducibility scaffold.}  The provision of
        manifest generation, repeated-run summaries, patient-level
        split audit, and an executable pipeline makes the study
        independently verifiable, a property that is increasingly
        valued in medical-imaging literature.

  \item \textbf{Prepared next-cohort resource.}  The mention of the
        prepared BIMCV-COVID19+ paired subset (638 COVID-positive
        subjects, 3,080 radiographs) is a concrete and useful
        pointer to the path toward a credible follow-up study.
\end{enumerate}

% =============================================================
\section{Major Weaknesses and Required Revisions}
\label{sec:major}
% =============================================================

Each item below constitutes a \emph{required} change before the
manuscript can be considered for acceptance.

% -----------------------------------------------------------
\subsection{[M1] Critically Insufficient Validation Cohort}
% -----------------------------------------------------------

\begin{majorbox}
\major{1}\ \
The primary paired validation split contains \textbf{four images} from
four patients — three positive and one negative.  The resampling study
improves the situation but each of the eight resamples still holds out
only \textbf{one negative patient}.  No metric computed on a single
negative example can be considered statistically meaningful, and the
authors' own Table~3 and Hypothesis H5 confirm that no result survives
balanced evaluation.  Publishing comparative deep-learning results on a
four-image test set, even as a ``feasibility screen'', sets a dangerous
precedent and falls below the minimum evidential standard for \tcsvt{}.
\end{majorbox}

\textbf{Required action:} The authors must either (a) incorporate the
prepared BIMCV-COVID19+ subset alongside a cross-source non-COVID
control to provide a validation cohort with at least 50 patients and a
positive/negative ratio no worse than 4:1, or (b) restructure the
submission as a methodological/benchmarking paper whose primary
contribution is the evaluation \emph{protocol} itself, not the JDCNet
architecture.  Reporting comparative numbers on a four-image test set
in a transactions paper is not acceptable regardless of how many
caveats accompany the table.

% -----------------------------------------------------------
\subsection{[M2] Proposed Architecture Underperforms All Baselines}
% -----------------------------------------------------------

\begin{majorbox}
\major{2}\ \
The full JDCNet stack (DPE + MHRA + DFPN) does not outperform the
stripped-down plain cross-modal logit-KD baseline on any metric under
either evaluation regime; under the primary resampling protocol, it also
underperforms student-only training on balanced accuracy (0.546 vs.\
0.636) and MCC (0.061 vs.\ 0.209).  The progressive complexity
experiment (Appendix, Table A5) further shows a \emph{non-monotonic}
degradation: each added module reduces mean paired-cohort performance
relative to the plain baseline.  In the current form, the paper
demonstrates that the proposed DPE, MHRA, and DFPN modules are harmful
under the present regime, which is a negative result that requires either
(a) a theoretical and/or empirical explanation for why the modules are
expected to help at larger scale, or (b) removal of the modules and
reframing around the plain logit-KD baseline as the technical
contribution.
\end{majorbox}

\textbf{Required action:}  Choose one of the following paths:
\begin{itemize}[leftmargin=2em,nosep]
  \item \textbf{Path A (Scale up):}  Validate the full module stack on
        the enlarged cohort described under M1. If the modules still do
        not contribute, remove them from the architecture claim entirely.
  \item \textbf{Path B (Reframe):}  Present the paper as a study of
        plain cross-modal logit-KD under patient-level paired evaluation,
        with DPE/MHRA/DFPN demoted to negative-result appendix material.
        In this case, the technical contribution is the evaluation
        protocol, the cross-source resampling methodology, and the
        published evidence-boundary analysis.
\end{itemize}

% -----------------------------------------------------------
\subsection{[M3] Absence of Comparison with State-of-the-Art Methods}
% -----------------------------------------------------------

\begin{majorbox}
\major{3}\ \
The paper includes no comparison with any published cross-modality
distillation or multi-modal medical-imaging method from the recent
literature.  The closest comparisons are (i) student-only training,
(ii) late fusion, (iii) same-modality KD, and (iv) generic attention
transfer/feature hint controls.  None of these is a \emph{published
baseline} from a named prior system.  For a \tcsvt{} submission, at
minimum the following categories of related work should yield
comparable baselines: (a) representation-alignment-based cross-modal
distillation (\eg{} Gupta \etal{} CVPR 2016; Nie \etal{} IEEE TMI 2017;
more recent modality-hallucination works), (b) at least one published
lightweight ResNet or MobileNet chest-X-ray classifier as a
single-modality anchor beyond the custom three-stage student backbone,
and (c) any existing published COVID-19 multi-modal study that reports
patient-level results on the same Cohen dataset.
\end{majorbox}

\textbf{Required action:}  Add at least three state-of-the-art baselines
from named prior systems.  If the paired cohort is too small for a fair
comparison with architectures designed for larger datasets, this
constraint must be explicitly discussed as a limitation of the study
design, not silently omitted.  Alternatively, use the BIMCV positive
paired subset to provide a sufficiently large evaluation context for
fair SOTA comparison.

% -----------------------------------------------------------
\subsection{[M4] Architectural Modules Lack Theoretical Justification}
% -----------------------------------------------------------

\begin{majorbox}
\major{4}\ \
The three proposed modules — DPE, MHRA, and DFPN — are introduced in
Section~3 without any theoretical motivation or ablative justification
beyond the observation that they are ``optional, testable complexity
increments.''  The appendix confirms that DPE is a $1{\times}1$
convolution with spatial softmax reweighting, MHRA is batch-first
multi-head attention with a sigmoid retain gate, and DFPN is a
three-scale top-down FPN.  None of these design choices is grounded in:
(a) a specific property of CT-to-X-ray modality gap that makes them
necessary, (b) a comparison with more standard alternatives (\eg{}
sinusoidal/learned positional encodings for DPE; standard attention
without a retain gate for MHRA; standard FPN~\cite{lin2017fpn} for
DFPN), or (c) a formal argument for why the combination should
outperform logit-only KD.  Without this grounding, the modules remain
ad-hoc additions whose performance on larger cohorts cannot be
predicted.
\end{majorbox}

\textbf{Required action:}  For each proposed module, provide:
\begin{itemize}[leftmargin=2em,nosep]
  \item A one-paragraph theoretical motivation explaining \emph{why}
        the module is specifically useful for the CT-to-X-ray modality
        gap (\ie{} what property of the domain mismatch it addresses).
  \item A comparison with the most natural alternative design (\eg{}
        sinusoidal PE vs.\ DPE; standard MHA vs.\ MHRA with retain gate;
        standard FPN vs.\ DFPN).
  \item An acknowledgment of the non-monotonic progressive-complexity
        findings and a working hypothesis for when the module would be
        expected to become beneficial.
\end{itemize}
If no such justification can be provided, the modules should be demoted
to an appendix or removed entirely.

% -----------------------------------------------------------
\subsection{[M5] Training Protocol is Insufficiently Justified}
% -----------------------------------------------------------

\begin{majorbox}
\major{5}\ \
The training protocol uses a $128{\times}128$ input resolution, 5
training epochs, and AdamW with a fixed learning rate of $3{\times}10^{-4}$
and no learning-rate schedule.  These choices are not justified.
Five epochs is likely insufficient for convergence of any of the module-
augmented variants, especially under the severe class imbalance of the
paired cohort.  The $128{\times}128$ resolution discards substantial
diagnostic resolution available in chest radiographs (standard clinical
resolution is typically $1024{\times}1024$ or higher, and even
research-grade inputs commonly use $224{\times}224$ or $512{\times}512$).
The uniform $3{\times}10^{-4}$ learning rate without warm-up or decay
is a non-standard choice for medical image classification.  These
limitations may be contributing to the negative performance of the
proposed modules, independently of the data size problem.
\end{majorbox}

\textbf{Required action:}  Either (a) justify each training choice
with a clear rationale (\eg{} constrained compute, convergence analysis,
or sensitivity study showing that increasing epochs or resolution does
not change the ranking), or (b) re-run experiments with at least
$224{\times}224$ resolution, a cosine-decay schedule over 30--50 epochs,
and report whether the negative-module finding persists.  Any claim that
results are limited by ``data scarcity rather than hyperparameter
sensitivity'' (currently made in Section~4.5) must be supported by a
convergence curve showing that 5 epochs is sufficient for these
architectures.

% -----------------------------------------------------------
\subsection{[M6] Scope Fit with IEEE TCSVT}
% -----------------------------------------------------------

\begin{majorbox}
\major{6}\ \
IEEE TCSVT focuses on circuits, systems, and algorithms for video
technology. The submitted manuscript analyzes single still chest images
(X-ray and CT axial slices) and does not engage with any video-specific
aspects: temporal modeling, inter-frame consistency, video-based
physiological monitoring, or similar. The paper's framing as a ``pilot
study'' with primarily negative results further weakens the
contributions relative to TCSVT's standard expectation of technically
validated methods with demonstrated improvements.  The authors should
provide an explicit paragraph addressing TCSVT scope: either (a)
explain the relevance to video-technology circuits and systems (\eg{}
real-time inference pipeline, edge-deployable lightweight network),
or (b) consider targeting a more directly relevant venue such as
\textit{IEEE Transactions on Medical Imaging} (TMI),
\textit{Medical Image Analysis} (MedIA), or
\textit{IEEE Journal of Biomedical and Health Informatics} (JBHI).
\end{majorbox}

\textbf{Required action:}  Add a paragraph in the Introduction or
Conclusion explicitly connecting the technical contributions
(lightweight cross-modal distillation, deployment-realistic inference
architecture, edge-deployable student backbone) to TCSVT's scope in
video-based health monitoring, portable imaging systems, or
real-time deployment circuits. Alternatively, the handling editor
should advise whether the submission falls within TCSVT's scope.

% =============================================================
\section{Minor Weaknesses and Suggested Revisions}
\label{sec:minor}
% =============================================================

The following items are important but not individually blocking.  They
should all be addressed in a revision.

% -----------------------------------------------------------
\subsection{Related Work}
% -----------------------------------------------------------

\begin{minorbox}
\minor{1}\ \
The Related Work section is disproportionately dominated by COVID-19
classification papers from 2020–2022.  For a 2026 submission to a
major transactions journal, the following literature gaps should
be addressed:
\end{minorbox}

\begin{enumerate}[label=(\alph*),leftmargin=2em]
  \item \textbf{Modern backbone baselines.}  Vision Transformers
        (ViT~\cite{dosovitskiy2020image}), Swin Transformer
        \cite{liu2021swin}, and DeiT are cited or in-scope but none
        is used as a student or teacher backbone.  The related work
        should explain why lightweight CNNs rather than ViT-based
        architectures were chosen for the low-resolution, small-cohort
        regime.
  \item \textbf{Recent cross-modal distillation.}  The cross-modal
        distillation literature has advanced substantially since
        Gupta~\etal{} (CVPR 2016).  Recent works on RGB-depth, CT-PET,
        and MRI-X-ray cross-modal supervision (\eg{} via contrastive
        alignment, CLIP-style pretraining, or paired embedding spaces)
        should be surveyed.
  \item \textbf{Contrastive and self-supervised medical representations.}
        Self-supervised pretraining on chest X-rays (\eg{}
        MoCo/SimCLR applied to CheXpert or MIMIC-CXR) is now standard
        practice and directly relevant to the student initialization
        question, but is absent from the related work.
  \item \textbf{LUPI and modality dropout.}  The paper cites
        Vapnik \& Vashist (2009) and Lopez-Paz~\etal{} (2016) on LUPI
        but omits more recent works on modality dropout and
        missing-modality robustness (\eg{} Neverova~\etal{} 2016;
        Cheerla \& Gevaert 2019; Ma~\etal{} 2021), which are directly
        in scope.
  \item \textbf{Feature-level cross-modal distillation in medical
        imaging.}  Nie~\etal{} (TMI 2017) on cross-modality image
        synthesis via GAN, and Chartsias~\etal{} on modality
        synthesis/transfer in cardiac imaging, are relevant but not
        cited.
\end{enumerate}

% -----------------------------------------------------------
\subsection{Presentation and Structure}
% -----------------------------------------------------------

\begin{minorbox}
\minor{2}\ \
The paper contains excessive repetition of the same cautions and
disclaimers across the abstract, introduction, Section 3, Section 4,
Table 1, Table 3, and the conclusion.  The phrase ``tiny paired
cohort'' appears 17 times in the main text.  While the authors' caution
is appreciated, this repetition reduces readability and should be
consolidated into one clearly placed disclaimer per section boundary.
\end{minorbox}

\begin{minorbox}
\minor{3}\ \
Table~1 (Problem Scope) provides useful orientation, but it occupies
nearly a full double-column width and uses a very wide second column
at the expense of clearly formatted rows.  This table would be more
readable as a compact two-column list or a narrower single-column table
with paragraph breaks reduced to keywords.
\end{minorbox}

\begin{minorbox}
\minor{4}\ \
Figure 1 (architecture overview) is described in the caption and text
as a system diagram, but the per-module dimensions, number of parameters,
and channel widths are provided only in the appendix.  For a
transactions paper, the architecture figure should include sufficient
technical detail (channel dimensions, skip-connection types,
normalization layers) to allow independent reproduction without
consulting the appendix.
\end{minorbox}

\begin{minorbox}
\minor{5}\ \
Section~3 (Methodology) uses DPE, MHRA, and DFPN as if they are
well-established named modules, but these acronyms are coined by the
authors themselves.  The section should explicitly state this and
provide a clearer separation between (a) the core cross-modal KD
objective (which is standard) and (b) the novel optional modules
(which are the paper's architectural contribution, however negative
the evidence for them turns out to be).
\end{minorbox}

\begin{minorbox}
\minor{6}\ \
The distillation objective in Equation~(1) uses the KL divergence in
the direction $\mathrm{KL}(\text{teacher}\|\text{student})$ rather
than the standard Hinton direction $\mathrm{KL}(\text{teacher}\|
\text{student})$ or the symmetric form.  The choice of direction is
not discussed.  For clarity, the authors should state which direction
is used and whether alternative directions were evaluated.
\end{minorbox}

% -----------------------------------------------------------
\subsection{Experimental Protocol}
% -----------------------------------------------------------

\begin{minorbox}
\minor{7}\ \
The hyperparameter ablation in Section~4.5 sweeps temperature
$T \in \{2,4,6\}$ and $\alpha \in \{0.3,0.6,0.9\}$ but omits the
most commonly reported standard values ($T=1$, which reduces to
hard-label KD, and $\alpha=1.0$, which is pure KD).  Including $T=1$
is important to confirm that the distillation effect is real rather
than an artifact of softening.
\end{minorbox}

\begin{minorbox}
\minor{8}\ \
The attention-transfer and feature-hint baselines described as
``mechanism controls'' in Section~4.4 are not accompanied by
implementation details in the main text.  The appendix provides
a brief mention but does not specify: (a) at which layer the attention
maps are extracted, (b) what spatial resolution is used for the hint
projector, or (c) what weighting is applied to the alignment loss
relative to the cross-entropy and KL terms.  A one-paragraph
description in the main methodology section is required.
\end{minorbox}

\begin{minorbox}
\minor{9}\ \
The late-fusion baseline is described as using ``paired CT and X-ray
inputs at training and inference''.  This makes it a strictly different
deployment scenario than the student-only and KD variants (which are
X-ray only at inference), and the paper correctly acknowledges this.
However, Table~3 (primary resampling table) lists late fusion alongside
X-ray-only methods without a visual separator or column flag indicating
the inference-modality difference.  A footnote or a separate sub-table
for the deployment-realistic X-ray-only variants is needed to prevent
readers from treating late fusion as a direct competitor.
\end{minorbox}

\begin{minorbox}
\minor{10}\ \
No learning-curve plots are provided.  Given that only 5 epochs are
used and the authors claim the performance plateau is due to data
scarcity rather than non-convergence, training and validation loss
curves for at least the student-only, plain cross-modal KD, and
full JDCNet variants should be shown in the appendix.
\end{minorbox}

\begin{minorbox}
\minor{11}\ \
The paper uses the terms ``knowledge distillation'' and
``cross-modal distillation'' interchangeably throughout, but in the
experimental tables uses the abbreviations ``KD'', ``logit KD'',
``same-modality KD'', and ``cross-modality KD'' inconsistently.
A glossary table or a consistent abbreviation scheme should be
established in Section~3 and applied uniformly.
\end{minorbox}

% -----------------------------------------------------------
\subsection{Quantitative Reporting}
% -----------------------------------------------------------

\begin{minorbox}
\minor{12}\ \
Several numeric entries in Table~4 (resampling primary evidence)
show standard deviations of 0.000 (\eg{} plain cross-modal logit KD:
balanced accuracy $0.500 \pm 0.000$, specificity $0.000 \pm 0.000$
across all eight resamples).  This is highly unusual for a stochastic
process and suggests that the model is collapsing to a trivial
all-positive prediction regime with zero variance.  The authors should
explicitly confirm this interpretation and provide a plot of per-split
positive-prediction rate to make the trivial-prediction collapse
visually evident.  Reporting metrics with $\pm 0.000$ without
explanation is potentially misleading.
\end{minorbox}

\begin{minorbox}
\minor{13}\ \
The paper reports ROC-AUC in the per-seed appendix table (Table A2)
but PR-AUC in the primary resampling table (Table~4).  This
inconsistency makes cross-table comparison difficult.  Either both
tables should report the same AUC variant, or the discrepancy should
be explicitly noted with a justification.
\end{minorbox}

\begin{minorbox}
\minor{14}\ \
The progressive complexity experiment (Appendix Table A5 /
Section~4.5) shows that ``+DPE'' has the same parameter count (0.484M)
as ``Plain logit KD''.  Since DPE is described as a $1{\times}1$
convolution with spatial softmax, this seems plausible but should be
explained: either DPE replaces rather than adds parameters, or the
reported parameter counts are approximate and the $1{\times}1$
convolution weight contribution is below rounding precision.
\end{minorbox}

% -----------------------------------------------------------
\subsection{Claims and Framing}
% -----------------------------------------------------------

\begin{minorbox}
\minor{15}\ \
The abstract states ``plain cross-modal logit-KD control attains the
highest mean result on the four-image validation subset (0.875
accuracy and 0.714 macro-F1)''.  Given that accuracy of 0.875 on a
four-image set means exactly 3.5 images correct on average, this
number provides zero statistical information and should not be
reported as a meaningful comparative result in the abstract.  The
abstract should foreground the resampling-based primary evidence
rather than the fixed-split screen.
\end{minorbox}

\begin{minorbox}
\minor{16}\ \
The title uses the phrase ``Evidence-Bounded Reproducible Pilot Study''.
While accurate, this framing signals to reviewers and readers that the
paper is a negative or preliminary result.  For a transactions
submission, the title should instead foreground the methodological
contribution (\eg{} the evaluation protocol, the cross-modal distillation
framework, or the reproducible benchmark infrastructure) rather than
explicitly advertising the study as incomplete.
\end{minorbox}

\begin{minorbox}
\minor{17}\ \
The paper explicitly states (Section~3.2) that ``DPE, MHRA, and DFPN
are retained as optional, testable complexity increments rather than as
validated gains.''  This unusual sentence in a methodology section
effectively pre-emptively refutes the paper's own architectural
contribution.  Either the modules are part of the contribution and
should be described with appropriate scientific confidence, or they are
negative-result artifacts and should be moved to the appendix with
that framing made explicit in the abstract.
\end{minorbox}

% -----------------------------------------------------------
\subsection{Dataset and Preprocessing}
% -----------------------------------------------------------

\begin{minorbox}
\minor{18}\ \
The paired cohort matching strategy is described as ``match each
X-ray to the closest available CT from the same patient using the
reported temporal offset when available.''  The details of this
matching are critical: (a) what is the median temporal offset between
matched pairs? (b) how many pairs were matched exactly versus
approximately? (c) is there a threshold on acceptable temporal offset?
A disease like COVID-19 can progress rapidly, so a multi-week offset
between the X-ray and CT acquisition dates would substantially
invalidate the pairing assumption.
\end{minorbox}

\begin{minorbox}
\minor{19}\ \
The data preprocessing section mentions normalization of the modality
field and exclusion of ``todo'' findings, but does not describe:
(a) whether any image-level preprocessing (\eg{} CLAHE, histogram
equalization, Hounsfield unit windowing for CT) was applied,
(b) what CT plane (axial/coronal/sagittal) was selected, and
(c) whether multi-slice CT volumes were reduced to a single representative
slice and, if so, by what criterion.  These choices can substantially
affect CT classification performance.
\end{minorbox}

\begin{minorbox}
\minor{20}\ \
The all-CT manifest (63 images, 25 patients, 59 positives, 4 negatives)
is described as ``heavily imbalanced'' but appears in the paper
primarily as a data-availability reference.  The paper should
explicitly confirm whether any of the CT images used as teacher
training data are also represented in the paired-cohort X-ray training
set at the patient level, or whether the cohorts are completely
disjoint.
\end{minorbox}

% -----------------------------------------------------------
\subsection{Writing Quality and Terminology}
% -----------------------------------------------------------

\begin{minorbox}
\minor{21}\ \
Several sentences in the main text are excessively long and
multi-clausal.  For example, the last sentence of Section 4.4
(``PR-AUC remains comparatively high\ldots'') spans more than 80 words
and embeds three separate qualifications.  \tcsvt{} recommends concise,
direct technical writing.  Please revise paragraphs with sentences
exceeding 50 words.
\end{minorbox}

\begin{minorbox}
\minor{22}\ \
The term ``same-case'' is used throughout (\eg{} ``same-case
resampling'', ``same-case comparisons'', ``same-case evidence'') but
is not defined.  The authors appear to mean ``within each resample,
all models are evaluated on the same set of held-out patients,''
which is a property of the evaluation protocol, not of the cases
themselves.  The more standard term for this is \emph{paired
comparison} or \emph{blocked evaluation}.  Using ``same-case'' as a
technical term without definition risks misinterpretation.
\end{minorbox}

\begin{minorbox}
\minor{23}\ \
Section~4.7 (Limitations and Future Work) is well written but at
1,100 words is arguably longer than any of the methodology subsections.
The limitations could be reorganized as a compact bulleted list
followed by a focused ``minimum next experiment'' paragraph, which
is already present in the appendix.  The main-text limitations
section should be no longer than 400--500 words.
\end{minorbox}

% -----------------------------------------------------------
\subsection{References}
% -----------------------------------------------------------

\begin{minorbox}
\minor{24}\ \
Several references are listed as arXiv preprints despite having
appeared in peer-reviewed venues.  Specifically:
Dosovitskiy~\etal{} (ViT) was published at ICLR 2021;
Romero~\etal{} (FitNets) was published at ICLR 2015;
Rajpurkar~\etal{} (CheXNet) was later included in proceedings.
All references should be updated to the published version where
available, as per IEEE style guidelines.
\end{minorbox}

\begin{minorbox}
\minor{25}\ \
The reference list is missing several key works that are directly
relevant and frequently cited in the cross-modal distillation and
medical-imaging literature:
\end{minorbox}
\vspace{-6pt}
\begin{itemize}[leftmargin=2em,nosep]
  \item Lin~\etal{}, ``Feature Pyramid Networks for Object Detection,''
        CVPR 2017 — relevant to the DFPN design.
  \item Liu~\etal{}, ``Swin Transformer,'' ICCV 2021 — relevant to
        modern backbone choice discussion.
  \item Nie~\etal{}, ``Medical Image Synthesis with Context-Aware GAN,''
        IEEE TMI 2018 — directly relevant cross-modal synthesis baseline.
  \item D'Amour~\etal{}, ``Underspecification Presents Challenges for
        Credibility in Modern Machine Learning,'' NeurIPS 2022 —
        relevant to the underspecification argument in Section 1.3.
  \item Tian~\etal{}, ``Contrastive Representation Distillation,''
        ICLR 2020 — a significant advance in feature-level KD that
        should appear in the Related Work.
  \item Romanov \& Shivade, MIMIC-Extract, or similar structured
        electronic health record + imaging linkage studies, for
        motivating patient-level pairing.
\end{itemize}

% =============================================================
\section{Editorial and Typographic Comments}
\label{sec:editorial}
% =============================================================

\begin{enumerate}[leftmargin=2em]
  \item \typog{1}\ Line 213 (Figure 1 caption): the tab character
        between ``\texttt{CT-to-X-ray}'' and ``\texttt{knowledge}''
        produces irregular spacing in the compiled PDF; replace with
        a space.
  \item \typog{2}\ Table~2 (dataset protocol): the column header
        ``Positives'' should read ``COVID-Positive'' and ``Negatives''
        should read ``COVID-Negative'' for unambiguous interpretation.
  \item \typog{3}\ Equation~(1): the $\alpha$ balancing term and the
        $T^2$ gradient-scaling factor are both standard, but the
        equation currently combines them across a multi-line
        \texttt{aligned} environment in a way that makes the scope
        of the KL term ambiguous.  Consider using
        $\mathrm{KL}\!\bigl(\cdot \| \cdot\bigr)$ with large
        delimiters on a single line.
  \item \typog{4}\ Appendix, Table A2 (per-seed results):  seeds 42
        and 43 show identical results for all five models, which is
        statistically possible but warrants a note confirming this
        is not a copy-paste error.
  \item \typog{5}\ The appendix document class uses
        \verb|\documentclass[10pt,journal,compsoc]{IEEEtran}| while
        the main paper uses \verb|\documentclass[journal]{IEEEtran}|
        with a custom build path.  The two document classes should
        be consistent to ensure uniform typographic appearance when
        compiled together.
  \item \typog{6}\ Abbreviation ``KD'' is defined in the abstract
        but ``logit KD'', ``plain KD'', and ``cross-modal KD'' are
        used as distinct variants without a consolidated definition
        table.  A glossary of abbreviations used in tables would
        significantly improve readability.
  \item \typog{7}\ Section~3.2 and Section~4.1 both introduce
        ``Figure~\ref{fig:jdcnet}'' and ``Table~\ref{tab:problem_scope}''
        with nearly identical sentences.  The repeated cross-reference
        text should be consolidated.
\end{enumerate}

% =============================================================
\section{Summary Score Table}
\label{sec:scores}
% =============================================================

\begin{table}[h!]
\centering
\caption{Reviewer score breakdown (IEEE TCSVT standard rubric).
Scores are on a 1--5 scale: 5 = Excellent, 4 = Good,
3 = Acceptable, 2 = Below threshold, 1 = Reject.}
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{lcc}
\toprule
\textbf{Criterion} & \textbf{Score} & \textbf{Comment} \\
\midrule
Technical quality          & 2 & Critically insufficient validation data \\
Originality / novelty      & 2 & Modules do not outperform baselines \\
Significance of results    & 2 & All five hypotheses unsupported \\
Clarity of presentation    & 3 & Honest but repetitive and over-caveated \\
Completeness of experiments & 2 & No SOTA comparison; 4-image test set \\
Relevance to TCSVT scope   & 2 & Needs explicit scope justification \\
Reproducibility            & 5 & Exemplary: full pipeline and audit trail \\
Related work coverage      & 3 & COVID-centric; missing key KD literature \\
\midrule
\textbf{Overall recommendation} &
\multicolumn{2}{l}{\textbf{\color{warnorange}Major Revision Required}} \\
\bottomrule
\end{tabular}
\end{table}

% =============================================================
\section{Prioritized Action Plan for Authors}
\label{sec:actionplan}
% =============================================================

The following ordered list represents the minimum work required for
the revised manuscript to be considered for re-review.  Actions are
ordered by blocking priority.

\vspace{6pt}
\begin{infobox}
\textbf{Tier~1 — Blocking (must be resolved before re-review):}
\begin{enumerate}[leftmargin=1.5em,nosep]
  \item[\textbf{A1.}] Enlarge the paired validation cohort to at least
        50 patients with an acceptable positive/negative ratio
        ($\leq$ 4:1), or restructure the submission around the
        evaluation-protocol contribution and demote all comparative
        metrics to illustrative examples.
  \item[\textbf{A2.}] Add at least three published state-of-the-art
        baselines (at least one named published cross-modal distillation
        system and at least one published single-modality chest-X-ray
        classifier beyond the custom student backbone).
  \item[\textbf{A3.}] Either validate the DPE/MHRA/DFPN modules on a
        sufficiently sized cohort, or demote them to appendix-level
        negative results and remove all architecture-contribution
        language from the abstract, introduction, and conclusion.
  \item[\textbf{A4.}] Add explicit scope justification connecting the
        work to IEEE TCSVT's video-technology remit.
\end{enumerate}
\end{infobox}

\vspace{6pt}
\begin{infobox}
\textbf{Tier~2 — Required (must be addressed in revision):}
\begin{enumerate}[leftmargin=1.5em,nosep]
  \item[\textbf{B1.}] Justify training protocol: input resolution,
        number of epochs, and learning-rate schedule.
  \item[\textbf{B2.}] Provide training-loss convergence curves.
  \item[\textbf{B3.}] Provide implementation details for attention
        transfer and feature-hint baselines in the main text.
  \item[\textbf{B4.}] Clarify the CT–X-ray temporal pairing
        criterion and report the median temporal offset.
  \item[\textbf{B5.}] Describe CT preprocessing choices (HU
        windowing, slice selection criterion).
  \item[\textbf{B6.}] Update arXiv references to published versions
        (ViT $\to$ ICLR 2021; FitNets $\to$ ICLR 2015; etc.).
  \item[\textbf{B7.}] Add the five missing references identified in
        Minor~25.
\end{enumerate}
\end{infobox}

\vspace{6pt}
\begin{infobox}
\textbf{Tier~3 — Strongly recommended:}
\begin{enumerate}[leftmargin=1.5em,nosep]
  \item[\textbf{C1.}] Revise the title to foreground the protocol or
        framework contribution rather than the ``pilot study'' framing.
  \item[\textbf{C2.}] Reduce main-text repetition of cautions
        (``tiny paired cohort'' appears 17+ times); consolidate into
        structured limitation statements.
  \item[\textbf{C3.}] Foreground resampling-based metrics in the
        abstract instead of the four-image fixed-split results.
  \item[\textbf{C4.}] Separate late-fusion rows from deployment-
        realistic X-ray-only rows in Table~4.
  \item[\textbf{C5.}] Provide a per-split positive-prediction-rate
        plot to explain the $\pm 0.000$ standard deviation
        observations for trivial-collapse models.
\end{enumerate}
\end{infobox}

% =============================================================
\section{Additional References Recommended for Inclusion}
\label{sec:refs}
% =============================================================

The following references are recommended for inclusion in the revised
manuscript.  All entries are formatted in IEEE BibTeX style.

\begin{verbatim}
@inproceedings{liu2021swin,
  title={{Swin Transformer}: Hierarchical Vision Transformer
         Using Shifted Windows},
  author={Liu, Ze and Lin, Yutong and Cao, Yue and Hu, Han and
          Wei, Yixuan and Zhang, Zheng and Lin, Stephen and Guo,
          Baining},
  booktitle={Proceedings of the IEEE/CVF International Conference
             on Computer Vision (ICCV)},
  pages={10012--10022},
  year={2021},
  doi={10.1109/ICCV48922.2021.00986}
}

@inproceedings{lin2017fpn,
  title={Feature Pyramid Networks for Object Detection},
  author={Lin, Tsung-Yi and Doll{\'a}r, Piotr and Girshick, Ross
          and He, Kaiming and Hariharan, Bharath and Belongie,
          Serge},
  booktitle={Proceedings of the IEEE Conference on Computer Vision
             and Pattern Recognition (CVPR)},
  pages={2117--2125},
  year={2017},
  doi={10.1109/CVPR.2017.106}
}

@inproceedings{tian2020contrastive,
  title={Contrastive Representation Distillation},
  author={Tian, Yonglong and Krishnan, Dilip and Isola, Phillip},
  booktitle={International Conference on Learning Representations
             (ICLR)},
  year={2020},
  url={https://openreview.net/forum?id=SkgpBJrtvS}
}

@article{nie2018medical,
  title={Medical Image Synthesis With Context-Aware Generative
         Adversarial Networks},
  author={Nie, Dong and Trullo, Roger and Lian, Jun and Wang,
          Li and Petitjean, Caroline and Ruan, Su and Wang, Qian
          and Shen, Dinggang},
  journal={IEEE Transactions on Medical Imaging},
  volume={37},
  number={10},
  pages={2259--2269},
  year={2018},
  doi={10.1109/TMI.2018.2825371}
}

@inproceedings{damour2022underspecification,
  title={Underspecification Presents Challenges for Credibility
         in Modern Machine Learning},
  author={D'Amour, Alexander and Heller, Katherine A. and
          Moldovan, Dan and Adlam, Ben and Alipanahi, Babak and
          Beutel, Alex and Chen, Christina and Deaton, Jonathan
          and Eisenstein, Jacob and Hoffman, Matthew D. and others},
  booktitle={Journal of Machine Learning Research},
  volume={23},
  number={226},
  pages={1--61},
  year={2022}
}

@inproceedings{dosovitskiy2021iclr,
  title={An Image Is Worth 16x16 Words: Transformers for Image
         Recognition at Scale},
  author={Dosovitskiy, Alexey and Beyer, Lucas and Kolesnikov,
          Alexander and Weissenborn, Dirk and Zhai, Xiaohua and
          Unterthiner, Thomas and Dehghani, Mostafa and Minderer,
          Matthias and Heigold, Georg and Gelly, Sylvain and
          Uszkoreit, Jakob and Houlsby, Neil},
  booktitle={International Conference on Learning Representations
             (ICLR)},
  year={2021},
  url={https://openreview.net/forum?id=YicbFdNTTy}
}

@inproceedings{romero2015fitnets,
  title={{FitNets}: Hints for Thin Deep Nets},
  author={Romero, Adriana and Ballas, Nicolas and Kahou,
          Samira Ebrahimi and Chassang, Antoine and Gatta,
          Carlo and Bengio, Yoshua},
  booktitle={International Conference on Learning Representations
             (ICLR)},
  year={2015},
  url={https://arxiv.org/abs/1412.6550}
}

@article{zhou2021domain,
  title={Domain Generalization in Medical Imaging: A Survey},
  author={Zhou, Kaiyang and Liu, Ziwei and Qiao, Yu and Xiang,
          Tao and Loy, Chen Change},
  journal={arXiv preprint arXiv:2103.09573},
  year={2021}
}

@article{oakdenrayner2019hidden,
  title={Hidden Stratification Causes Clinically Meaningful
         Failures in Machine Learning for Medical Imaging},
  author={Oakden-Rayner, Luke and Dunnmon, Jared and Carneiro,
          Gustavo and R{\'e}, Christopher},
  journal={Proceedings of the ACM Conference on Health,
           Inference, and Learning (CHIL)},
  pages={151--159},
  year={2020},
  doi={10.1145/3368555.3384468}
}
\end{verbatim}

% =============================================================
\section{Final Remarks to the Handling Editor}
% =============================================================

This manuscript demonstrates a commendable level of scientific
transparency and reproducibility.  The authors have clearly invested
significant effort in making their experimental pipeline auditable and
in honestly reporting negative results.  However, the combination of
(a) a validation cohort of four images, (b) an architecture that
underperforms all simpler baselines, (c) the absence of any
state-of-the-art comparison, and (d) a ``pilot study'' framing that
does not meet the \tcsvt{} contribution threshold means that the
current submission is not yet ready for publication in a major
transactions journal.

The core scientific question — whether CT can serve as training-only
supervision for X-ray deployment under tiny paired cohorts — is
genuinely important and timely.  If the authors can incorporate the
BIMCV-COVID19+ positive paired subset alongside a matched negative
control, run the full comparison protocol with SOTA baselines on this
larger cohort, and validate or discard the DPE/MHRA/DFPN modules with
appropriate evidence, the revised submission would likely represent a
strong and publishable contribution to the cross-modal medical
imaging community.

The handling editor should consider whether IEEE TCSVT or a more
directly relevant venue (\eg{} IEEE TMI, MedIA, JBHI) is the
optimal home for this work pending revision.

\vspace{12pt}
\hrule
\vspace{6pt}
{\small\color{gray}
End of review report.  All comments are intended to be constructive.
The reviewer thanks the authors for their transparency in reporting
negative findings.}

\end{document}
